### 2016-01-12 p01-ch02-2013/paper.tex
Add publication information to chapter abstracts
Remove all `vspace`

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
\vspace{-20pt}
\begin{lstlisting}[float=h, label=lst:try:catch, caption=Using try-catch for processing future values]
try {
	x = f.get(e)
	S_1
} catch(Exception x) {
	S_2
}
\end{lstlisting}
\vspace{-20pt}
For example, in Listing \ref{lst:try:catch}, if the \gett \space operation raises an exception  control,  is transferred to line (5);
otherwise, the execution continues in line (3). 
In the \jtt{catch} block, the programmer has also access to the occurred exception that can be 
any kind of exception including an exception that is caused by a missed deadline.
In general, any uncaught exception gives rise to abortion of the active process and is recorded by its future.
Exceptions in our actor-based model thus are propagated by futures.

@@

\begin{wrapfigure}{r}{0.4\textwidth}
\vspace{-40pt}
\begin{center}
\includegraphics[scale=0.4]{figs/DM}
\end{center}
\vspace{-20pt}
\caption{Fredhopper's Controller life cycle for remote data processing}
\label{fig:frh-dm}
\vspace{-10pt}
\end{wrapfigure}

@@

Listing \ref{lst:frh:polling} and \ref{lst:frh:deadlines} present the difference in the previous Controller and the approach in Crisp.
The left code snippet shows the Controller that uses polling to retrieve data processing results.
The right code snippet shows the one that uses messages with deadlines.
\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\vspace{-25pt}
\begin{lstlisting}[label=lst:frh:polling, caption=With polling]
class DataProcessor begin
	op process(d: Data) ==
		var p := allocDataProcessor(d)
		p ! process (d)
		do {
			s := p ! getStatus (d)
			if (s <> nil)
				var r := p ! getResults(d)
				publishResult(r)
			wait(TimeUnit.toSecond(1))
		} while (true)
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\vspace{-25pt}
\begin{lstlisting}[label=lst:frh:deadlines, caption=With deadlines]
class DataProcessor begin
	op process(d: Data) == 
		var p := allocDataProcessor(d)
		var D := estimateDeadline(d)
		var f := 
			p ! process (d) deadline (D)
		try {
			publishResult(f.get())
		} catch (Exception x) {
			if (f.isAborted)
				notifyFailure(d)
		}
end 
\end{lstlisting}
\end{minipage}
\vspace{-10pt}
\end{center}

@@

Additionally, on the data processing service node, the new implementation takes advantage of the extensibility of schedulers in Crisp.
As discussed above, the default scheduling policy used for each actor is EDF based on the deadlines carried by incoming messages to the actor.
However, this behavior may be extended and replaced by a custom implementation from the programmer.
In this case study, the priority of processes may differ if they the job request comes from specific customer; i.e.
apart from deadlines, some customers have priority over others because they require a more real-time action on their job requests while others run a more relaxed business model.
To model and implement this custom behavior, a custom scheduler is developed for the data processing node.
\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\vspace{-30pt}
\begin{lstlisting}[label=lst:frh:dm, caption=Data Processor class]
class DataProcessor begin
	var scheduler := new DataScheduler()
	op process(d: Data) ==
		// do process
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\vspace{-30pt}
\begin{lstlisting}[label=lst:frh:sched, caption=Custom scheduler]
class DataScheduler extends DefaultSchedulingManager {
	boolean isPrior(Process p1, Process p2) {
		if (p1.getCustomer().equals("A")) {
			return true;
		}
		return super.isPrior(p1, p2);
	}
}
\end{lstlisting}
\end{minipage}
\vspace{-15pt}
\end{center}
In the above listings, Listing \ref{lst:frh:sched} defines a custom scheduler that determines the priority of two processes with custom logic for specific customer.
To use the custom scheduler, the only requirement is that the class \jtt{DataProcessor} defines a specific class variable called \jtt{scheduler} in Listing \ref{lst:frh:dm}.
The \textsl{custom scheduler} is picked up by Crisp core architecture and is used to schedule the queued processes.
% In the listing, \jtt{DefaultSchedulingManager} denotes the default EDF scheduler that is implemented in Crisp.
Thus, all processes from customer \jtt{A} have priority over processes from other customers no matter what their deadlines are.

We use Controller's logs for the period of February and March 2013 to examine the evaluation of Crisp approach.
We define \emph{customer satisfaction} as a property that represents the effectiveness of futures with deadline.
\begin{wraptable}{l}{0.25\textwidth}
\vspace{-15pt}
\begin{tabular}{c c}\thickhline
$s_1$ & $s_2$ \\ \thickhline
$88.71\%$ & $94.57\%$ \\ \hline
\end{tabular}
\caption{Evaluation Results}
\label{tbl:eval}
\vspace{-15pt}
\end{wraptable}
For a customer $c$, the satisfaction can be denoted by $s = \frac{r^F_c}{r_c}$; in which $r^F_c$ is the number of finished data processing jobs and $r_c$ is the total number of requested data processing jobs from customer $c$. 
We extracted statistics for completed and never-ended data processing jobs from Controller logs ($s_1$).
We replayed the logs with Crisp approach and measured the same property ($s_2$).
We measured the same property for 180 customers that Fredhopper manages on the cloud.
In this evaluation, a total number of about 25000 data processing requests were included.
The results show $6\%$ improvement in Table \ref{tbl:eval} (that amounts to around 1600 better data processing requests). 
Because of data issues or wrong parameters in the data processing requests, there are requests that still fail or never end and should be handled by a human resource.

>>>>

\subparagraph*{Conference Publication}
\emph{Lecture Notes in Computer Science, Volume 7890, Coordination Models and Languages in 15th conference on Distributed Computing Techniques -- COORD 2013, Pages 181--195, DOI \smalltt{10.1007/978-3-642-38493-6\_13}}

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
% \vspace{-20pt}
\begin{lstlisting}[float=h, label=lst:try:catch, caption=Using try-catch for processing future values]
try {
	x = f.get(e)
	S_1
} catch(Exception x) {
	S_2
}
\end{lstlisting}
% \vspace{-20pt}

For example, in Listing \ref{lst:try:catch}, if the \gett \space operation raises an exception  control,  is transferred to line (5);
otherwise, the execution continues in line (3). 
In the \jtt{catch} block, the programmer has also access to the occurred exception that can be 
any kind of exception including an exception that is caused by a missed deadline.
In general, any uncaught exception gives rise to abortion of the active process and is recorded by its future.
Exceptions in our actor-based model thus are propagated by futures.

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.4\textwidth}
% \vspace{-40pt}
\begin{center}
\includegraphics[scale=0.4]{figs/DM}
\end{center}
% \vspace{-20pt}
\caption{Fredhopper's Controller life cycle for remote data processing}
\label{fig:frh-dm}
% \vspace{-10pt}
% \end{wrapfigure}
\end{figure}

@@

Listing \ref{lst:frh:polling} and \ref{lst:frh:deadlines} present the difference in the previous Controller and the approach in Crisp.
The left code snippet shows the Controller that uses polling to retrieve data processing results.
The right code snippet shows the one that uses messages with deadlines.

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=lst:frh:polling, caption=With polling]
class DataProcessor begin
	op process(d: Data) ==
		var p := allocDataProcessor(d)
		p ! process (d)
		do {
			s := p ! getStatus (d)
			if (s <> nil)
				var r := p ! getResults(d)
				publishResult(r)
			wait(TimeUnit.toSecond(1))
		} while (true)
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=lst:frh:deadlines, caption=With deadlines]
class DataProcessor begin
	op process(d: Data) == 
		var p := allocDataProcessor(d)
		var D := estimateDeadline(d)
		var f := 
			p ! process (d) deadline (D)
		try {
			publishResult(f.get())
		} catch (Exception x) {
			if (f.isAborted)
				notifyFailure(d)
		}
end 
\end{lstlisting}
\end{minipage}
% \vspace{-10pt}
\end{center}

@@

Additionally, on the data processing service node, the new implementation takes advantage of the extensibility of schedulers in Crisp.
As discussed above, the default scheduling policy used for each actor is EDF based on the deadlines carried by incoming messages to the actor.
However, this behavior may be extended and replaced by a custom implementation from the programmer.
In this case study, the priority of processes may differ if they the job request comes from specific customer; i.e.
apart from deadlines, some customers have priority over others because they require a more real-time action on their job requests while others run a more relaxed business model.
To model and implement this custom behavior, a custom scheduler is developed for the data processing node.

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=lst:frh:dm, caption=Data Processor class]
class DataProcessor begin
	var scheduler := new DataScheduler()
	op process(d: Data) ==
		// do process
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=lst:frh:sched, caption=Custom scheduler]
class DataScheduler extends DefaultSchedulingManager {
	boolean isPrior(Process p1, Process p2) {
		if (p1.getCustomer().equals("A")) {
			return true;
		}
		return super.isPrior(p1, p2);
	}
}
\end{lstlisting}
\end{minipage}
% \vspace{-15pt}
\end{center}

In the above listings, Listing \ref{lst:frh:sched} defines a custom scheduler that determines the priority of two processes with custom logic for specific customer.
To use the custom scheduler, the only requirement is that the class \jtt{DataProcessor} defines a specific class variable called \jtt{scheduler} in Listing \ref{lst:frh:dm}.
The \textsl{custom scheduler} is picked up by Crisp core architecture and is used to schedule the queued processes.
% In the listing, \jtt{DefaultSchedulingManager} denotes the default EDF scheduler that is implemented in Crisp.
Thus, all processes from customer \jtt{A} have priority over processes from other customers no matter what their deadlines are.

We use Controller's logs for the period of February and March 2013 to examine the evaluation of Crisp approach.
We define \emph{customer satisfaction} as a property that represents the effectiveness of futures with deadline.

\begin{table}[h]
% \begin{wraptable}{l}{0.25\textwidth}
% \vspace{-15pt}
\begin{tabular}{c c}\thickhline
$s_1$ & $s_2$ \\ \thickhline
$88.71\%$ & $94.57\%$ \\ \hline
\end{tabular}
\caption{Evaluation Results}
\label{tbl:eval}
% \vspace{-15pt}
% \end{wraptable}
\end{table}

For a customer $c$, the satisfaction can be denoted by $s = \frac{r^F_c}{r_c}$; in which $r^F_c$ is the number of finished data processing jobs and $r_c$ is the total number of requested data processing jobs from customer $c$. 
We extracted statistics for completed and never-ended data processing jobs from Controller logs ($s_1$).
We replayed the logs with Crisp approach and measured the same property ($s_2$).
We measured the same property for 180 customers that Fredhopper manages on the cloud.
In this evaluation, a total number of about 25000 data processing requests were included.
The results show $6\%$ improvement in Table \ref{tbl:eval} (that amounts to around 1600 better data processing requests). 
Because of data issues or wrong parameters in the data processing requests, there are requests that still fail or never end and should be handled by a human resource.
